Project assignment - Tahoe-LAFS with SHA-3 candidates

### 2010-12-15 paper/main.tex
Some corrections to discussion

\subsection{The candidates}
If we look primarily at the large file up/download we see that the candidates
that outperforms, or are close to outperforming \ac{SHA}-256 are BLAKE,
\ac{BMW}, Shabal, Simd and Luffa. The same is true if we eliminate the overhead
cause by our bindings for the small files. That only these five candidates
manages to outperform is expected from the \ac{SUPERCOP} results, REF, however
the order and proportion of the measurements does not. This is primarily
because we have not used the fastest implementation for all candidates, and the
relative speed of the chosen implementation compared to the fastest
implementation in \ac{SUPERCOP} differs (Table \ref{tbl:sha3:relativespeed}.
The performance of each candidate compared to the \ac{SHA}-256 version found in
Tahoe-\ac{LAFS} is also somewhat slower than you would expect. We blame this
mainly on our Cython-bindings and our skill. We believe a developer with more
knowledge of the inner workings of the implementations, the Python C-\ac{API}
and \ac{GCC} could have produced better results.

@@

\subsection{Optimizing results}
We have not used the fastest possible implementations possible for various
reasons mentioned previously. However, if we had actually used the fastest
implementations in \ac{SUPERCOP}, achieved median speed for every hash

\subsection{Theoretical optimized results}
We have not use the fastest available implementations for all of the
candidates, we also know that our bindings creates an overhead for all calls.
Therefore we have tried to calculate the results that could have been achieved
in Tahoe-\ac{LAFS} if we had managed to obtain the speeds of the fastest
implementations in \ac{SUPERCOP}. The results can be seen in appendix
\ref{appendix:optimzed_sha3}.

>>>>

\subsection{The candidates}

If we look primarily at the large file up/download we see that the candidates
that outperforms, or are close to outperforming double \ac{SHA}-256 are BLAKE,
\ac{BMW}, Shabal, Simd and Luffa. The same is true if we eliminate the overhead
cause by our bindings for the small files. That only these five candidates
manages to outperform double \ac{SHA}-256 is expected from the \ac{SUPERCOP}
results (\autoref{app:supercop:bench}) however the order and proportion of the
measurements is not. This reason for another order and relative speed is
primarily because we have not used the fastest implementation for all
candidates, and the relative speed of the chosen implementation compared to the
fastest implementation in \ac{SUPERCOP} differs (Table
\ref{tbl:sha3:speedrelative}.  The performance of each candidate compared to
the \ac{SHA}-256 version found in Tahoe-\ac{LAFS} is also somewhat slower than
you would expect. We blame this mainly on our Cython-bindings and our skill. We
believe a developer with more knowledge of the inner workings of the
implementations, the Python C-\ac{API} and \ac{GCC} could have produced better
results.

@@

\subsection{Theoretical optimized results}

We have not use the fastest available implementations for all of the
candidates, we also know that our bindings creates an overhead for all calls.
Therefore we have tried to calculate the results that could have been achieved
in Tahoe-\ac{LAFS} if we had managed to obtain the speeds of the fastest
implementations in \ac{SUPERCOP}. The results can be seen in
\autoref{appendix:optimzed_sha3}.
